### 2021-04-14 submissions/CPC_response_to_reviewers.md

2. Page 10, missing information on [INSERT RUNTIME COMPARISONS HERE].

	**This was a placeholder statement that should not have been included in the document. It has been removed.**

3. In Figure 2, the RCSLM seems to consistently perform better than WSGG, except in Example S2. In addition, WSGG performs worse than PM in Example S4. Can the authors explain why?

	**The PM and WSGG models are primarily empirical and contain very little representative physics, which could explain their unexpected behavior in Examples 2 and 4 but also makes it very difficult to find or treat sources of error. Any model, but especially empirical models, can behave unexpectedly when applied to conditions or parameters outside of those for which it was developed. The example cases are meant to be illusrative of the software's capabilities, not an evaluation of the models themselves, which is outside the scope of this paper. The reviewer's request for an explanation, however, is valid. A brief discussion has been added to Section 5 to address these specific discrepancies. Additional information about the specific limitations, strengths, and weaknesses associated with each model can be found in Section 2.**

@@

**The authors would like to thank the reviewer for their insightful comments and suggestions. As members of the combustion community, we heartily agree that a tool like RadLib could benefit researchers and facilitate radiation model development for combustion CFD.**

1) I could not successfully build and run the library in two different Linux systems. In both cases, first, the cmake returned an error:
"CMake Error at c++/CMakeLists.txt:34 (install): install TARGETS given no ARCHIVE DESTINATION for static library target "radlib"."
I could resolve this by adding ARCHIVE DESTINATION line on the c++/CMakeLists.txt file.
But, then on during "make" my installation was interrupted several times because of missing packages in my Python installation.
I would strongly recommend that the authors modify the installation instructions to include: a) list of dependencies (i.e., what compilers, what versions of python, what python packages, etc.), b) how to install the dependencies before building RadLib, c) a way to build RadLib with either only C++ or only Python. These installation notes do not necessarily need to be in the main manuscript, but they must be in the installation README of the code package.

2) The library includes PM, one WSGG, and a RCSLW model. The authors should clearly indicate the rationale of these choices (i.e., why only these three models) early on in the manuscript. Since this is intended for researchers who, presumably, are not experts in radiation modeling, the inclusion of these three models can be misleading. One might think that these three models are the most appropriate models for their simulations.

	**Section 2 has been heavily revised to address this issue. Each model's description now also includes a discussion of its strengths, weaknesses, and limitations when applied to combustion CFD in addition to the authors' rationale in choosing them for RadLib.**

@@

3) RadLib is intended to be expanded with new radiation property models in the future and interfaced with a user-supplied solver module for RTE. A brief discussion on how to interface such an external solver module should be presented. There is an example of a ray-tracing solver presented in the code files, but a brief discussion on coupling one's own RTE solver is important in the manuscript. Additionally, a brief discussion on how a user can add a new radiative property model should also be included.

	**Section 3 has been revised and extended to include more information on how users can include and interact with the RadLib library, including explicit references to example files that further illustrate usage of the library. Adding additional radiative property models to the RadLib library, however, is nontrivial, and we chose to move its discussion to the package documentation so as not to clutter the manuscript. This can be changed, if necessary, at the editor's discretion.**

@@

	**The authors purposely chose the TNF workshop data for calculating Planck Mean absorption coefficients because it is one of the most common and widely used radiation models applied to turbulent combustion simulations, despite its age and limitations. Section 2.1 has been revised to include a more explicit dicsussion of why the TNF radiation model was chosen and concerns related to its relative age and limited applicability. Section 4 includes example cases that clearly demonstrate the deficiencies of the PM model compared to the other models included with RadLib, and some additional discussion is available there.**

5) On page 13, the authors present a paragraph describing Figs. 2 and 3 - the comparison of various radiation property models present in RadLib in one-dimensional configurations. The comparisons are presented simply as observations without any explanation or reasoning why the models behave the way as seen in Fig. 2 and 3. If I understand correctly, the focus of the work presented here is not the comparison of the accuracy of the three models but to showcase the library. Therefore, these comparisons - specifically without any explanation of the results - may not be essential to the current manuscript, and can be shortened. These results do serve as descriptions of example cases provided in RadLib. On the same page, the authors say that "While ommitted [should be omitted] here for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in [11, 14] such that these examples also serve as a validation of the implementation of the
models." The authors should avoid qualitative description such as "essentially identical" in the context of validation and present a quantitative (e.g., % error) metric wherever possible. A strong validation is important for programs like this.

	**While it is true that the purpose of this paper is to present the RadLib library rather than evaluate or compare the models, the authors believe that example case results in Figures 2 and 3 are important to the illustration of RadLib's capabilities. The reviewer's point about presentation without explanation, however, is valid; to that end, the discussion in Section 5 has been expanded somewhat to acknowledge, if not fully explain or provide cause for, various features and descrepancies in the example case results. Due to the empirical nature of the PM and WSGG models, it is very difficult to identify, explain, or rectify unexpected behavior. It should be noted, however, that any model, and especially empirical models, can behave unpredictably when applied to parameter ranges or conditions outside of those for which is was developed.**

	**In regards to validation, the authors are unclear as to what the reviewer expects to see. RadLib's model implementations give results that are, in fact, essentially identical to those presented in the literature to within any visual margin. We do not have access to the data used to generate the plots in the literature, without which any quantitative measure of error is meaningless. We do, however, compare model results to the line-by-line data, which amounts to a direct solution of the RTE and is also identical to the line-by-line data in the literature (as expected). The authors believe that this serves as adequate validation of RadLib's model implementations given the lack of originial data for comparison.**
